Cocoa: Congestion Control Aware Queuing

### 2020-10-21 tex/figures/cocoa_common_beginning.tex
Readd cocoa_intervals

\documentclass{standalone}
\usepackage{libertine}
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usepackage{fix-cm}
\setlength{\parskip}{0pt}
\setlength{\baselineskip}{0pt}
%\usetikzlibrary{fit}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.shapes}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{intersections}
\usetikzlibrary{patterns}
\tikzset{%
  from end of path/.style={
    insert path={
      \pgfextra{%
        \expandafter\pgfprocesspathextractpoints%
          \csname tikz@intersect@path@name@#1\endcsname%
        \pgfpointlastonpath%
        \pgfgetlastxy\lastx\lasty
      }
      (\lastx,\lasty)
}}}
\tikzset{-dot-/.style={decoration={
  markings,
  mark=at position #1 with {\fill[color=red] circle (0.5mm);}},postaction={decorate}}}  
    \tikzset{
        hatch distance/.store in=\hatchdistance,
        hatch distance=10pt,
        hatch thickness/.store in=\hatchthickness,
        hatch thickness=2pt
    }
\begin{document}
\begin{tikzpicture}

>>>>

\documentclass{standalone}
\usepackage{libertine}
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usepackage{fix-cm}
\setlength{\parskip}{0pt}
\setlength{\baselineskip}{0pt}
%\usetikzlibrary{fit}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.shapes}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{intersections}
\usetikzlibrary{patterns}
\tikzset{%
  from end of path/.style={
    insert path={
      \pgfextra{%
        \expandafter\pgfprocesspathextractpoints%
          \csname tikz@intersect@path@name@#1\endcsname%
        \pgfpointlastonpath%
        \pgfgetlastxy\lastx\lasty
      }
      (\lastx,\lasty)
}}}
\tikzset{-dot-/.style={decoration={
  markings,
  mark=at position #1 with {\fill[color=red] circle (0.5mm);}},postaction={decorate}}}  
\tikzset{-dot3-/.style={decoration={
  markings,
  mark=at position #1 with {\draw[-,draw=none,fill=white](0.025,-0.05) -- (-0.025,0.05) -- (-0.015,0.05) -- (0.035,-0.05) -- cycle;%
\draw[-,color=black](0.025,-0.05) -- (-0.025,0.05); \draw[-,color=black](0.035,-0.05) -- (-0.015,0.05);}},postaction={decorate}}}
    \tikzset{
        hatch distance/.store in=\hatchdistance,
        hatch distance=10pt,
        hatch thickness/.store in=\hatchthickness,
        hatch thickness=2pt
    }
\begin{document}
\begin{tikzpicture}
